Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix spelling and reword paragraph.
s/forcible/forcibly/

Some of these sentences ran on a bit; I think the rewording is clearer, and is
almost exactly the same length.

One limitation of the Raft protocol is that if the cluster
membership drops from two nodes to one node then the cluster will
become unavailable without manual intervention. This is because when
there are two nodes in the cluster, both nodes are required for for
a majority vote and when one member is forcible shutdown then the
remaining cluster node will be unable to win elections or even commit
transaction entries and the cluster will become unavailable. There are
several options to get around this problem:

>>>>

One limitation of the Raft protocol is that if the cluster membership drops from
two nodes to one node, then the cluster will become unavailable without manual
intervention. This is because both nodes of a two-node cluster are required for
a majority vote.  When one member of a two-node cluster is forcibly shut down,
then the remaining cluster node will be unable to win elections or even commit
transaction entries, and the cluster will become unavailable. There are several
options to get around this problem:
